---
title: "Assignment 2 - Distributions and Proportions"
author: "Megan Willis-Jackson"
date: "9/16/2020"
output: 
  html_document: 
    theme: cerulean
    toc: yes
---

# Continuous Variables

The following code will call the libraries and data, and put the means, medians, standard deviations, 95% confidence intervals, and interquartile ranges for each of the continuous variables in one table.

```{r create table, message= FALSE, results='hide'}
library(readr)
library(ggplot2)
library(tidycensus)
library(tidyverse)
person_data <- read_csv("people.csv")[,2:6]
variables<- data.frame(c("Travel_Time","Household_Income","Housing_Cost"))
mean<- data.frame(c(mean(person_data$travel_time), mean(person_data$household_income), mean(person_data$monthly_housing_total)))
median<- data.frame(c(median(person_data$travel_time), median(person_data$household_income), median(person_data$monthly_housing_total)))
standard_deviation<- data.frame(c(sd(person_data$travel_time),sd(person_data$household_income),sd(person_data$monthly_housing_total)))
low_CI_95<- data.frame(c(1,1,1))
high_CI_95<- data.frame(c(1,1,1))
IQ_Range<- data.frame(c(IQR(person_data$travel_time),IQR(person_data$household_income),IQR(person_data$monthly_housing_total)))
summary_stats_contvar<- data.frame(c(variables,mean,standard_deviation,low_CI_95,high_CI_95,IQ_Range,median))
colnames(summary_stats_contvar)<- c("variable","mean","standard_deviation","low_CI_95","high_CI_95","IQ_Range","median")
rownames(summary_stats_contvar)<- summary_stats_contvar$variable
summary_stats_contvar<- summary_stats_contvar[,2:7]
```

```{r perform t tests for continuous variables}
summary_stats_contvar[1,3:4]<- t.test(person_data$travel_time,conf.level = .95)[["conf.int"]]
summary_stats_contvar[2,3:4]<- t.test(person_data$household_income,conf.level = .95)[["conf.int"]]
summary_stats_contvar[3,3:4]<- t.test(person_data$monthly_housing_total,conf.level = .95)[["conf.int"]]

knitr::kable(summary_stats_contvar, caption = "Summary Statistics for the Continuous Variables")

summary_stats_contvar
```

## Travel Time

```{r histograms - travel time}
paste("The average time it takes an MA resident in our sample to travel to work is about", prettyNum(summary_stats_contvar[1,1], digits = 2), "minutes. Half of the MA residents who commute have a commute longer than", prettyNum(median(person_data$travel_time, digits = 2)), "minutes, and half of them have a commute shorter than that. We can say with 95% confidence that the true mean travel time for the population of MA commuters is between", prettyNum(summary_stats_contvar[1,3], digits = 3), "and", prettyNum(summary_stats_contvar[1,4], digits = 3), "minutes. The distribution appears to be skewed right, which makes sense as people cannot have a negative commute time but commutes can sometimes be several hours long. There is a spike right around 60 minutes and another at 90 minutes, which also makes sense because for people with commutes around 55 or 65 minutes, when asked they would likely say 1 hour; same with 90 minutes - anything around that length and people would likely say an hour and a half.")

ggplot(person_data,
       aes(x = travel_time)) +
  geom_histogram() +
  scale_x_continuous(name = "Travel Time (minutes)") +
  scale_y_continuous(name = "Number of MA Residents in Sample") +
  theme_classic() +
  annotate("text", x = 50, y = 4000, size = 4,
           label = paste("Population mean (95% confidence):",
                         prettyNum(summary_stats_contvar[1,3], digits = 3),
                         "to",
                         prettyNum(summary_stats_contvar[1,4], digits = 3),
                         "minutes",
                         "\nSample mean:",
                         prettyNum(summary_stats_contvar[1,1], digits = 3),
                         "minutes",
                         "\nSample median:",
                         prettyNum(median(person_data$travel_time), digits = 3),
                         "minutes",
                         "\nSample standard deviation:",
                         prettyNum(summary_stats_contvar[1,2], digits = 3),
                         "minutes",
                         "\nSample interquartile range:",
                         prettyNum(quantile(person_data$travel_time)["25%"], digits = 4),
                         "to",
                         prettyNum(quantile(person_data$travel_time)["75%"], digits = 4),
                         "minutes"),
           hjust = 0, vjust = 1)

```


## Household Income

```{r histograms - household income}
paste("The average household income earned per year in our sample of MA residents is approximately $", prettyNum(summary_stats_contvar[2,1], digits = 2, big.mark = ","), ". Half of the MA residents are in households that earn more than $", prettyNum(median(person_data$household_income), digits = 2, big.mark = ","), "per year, and half of them are in households that earn less than that. We can say with 95% confidence that the true mean household income per year for the population of MA residents is between $", prettyNum(summary_stats_contvar[2,3], digits = 3, big.mark = ","), "and $", prettyNum(summary_stats_contvar[2,4], digits = 3, big.mark = ","), ". The distribution appears to be skewed right. This makes sense because the sample of MA residents here excludes anyone who does not have a positive income, whereas there is no cap on the highest income included.")

ggplot(person_data,
       aes(x = household_income)) +
  geom_histogram() +
  scale_x_continuous(name = "Household Income",
                     breaks = seq(0,1500000,by = 250000),
                     labels = c("$0","$250k","$500k","$750k","$1M","$1.25M","$1.5M")) +
  scale_y_continuous(name = "Number of MA Residents in Sample") +
  theme_classic() +
  annotate("text", x = 500000, y = 8000, size = 4,
           label = paste("Population mean (95% confidence): $",
                         prettyNum(summary_stats_contvar[2,3], digits = 3, big.mark = ","),
                         "to $",
                         prettyNum(summary_stats_contvar[2,4], digits = 3, big.mark = ","),
                         "\nSample mean: $",
                         prettyNum(summary_stats_contvar[2,1], digits = 3, big.mark = ","),
                         "\nSample median: $",
                         prettyNum(median(person_data$household_income), digits = 3, big.mark = ","),
                         "\nSample standard deviation: $",
                         prettyNum(summary_stats_contvar[2,2], digits = 3, big.mark = ","),
                         "\nSample interquartile range: $",
                         prettyNum(quantile(person_data$household_income)["25%"], digits = 4, big.mark = ","),
                         "to $",
                         prettyNum(quantile(person_data$household_income)["75%"], digits = 4, big.mark = ",")),
           hjust = 0, vjust = 1)

```

## Household Cost

```{r histograms - household Cost}
paste("The average cost of housing per month in our sample of MA residents is approximately $", prettyNum(summary_stats_contvar[3,1], digits = 2, big.mark = ","), ". Half of the MA residents are in households that cost more than $", prettyNum(median(person_data$monthly_housing_total), digits = 2, big.mark = ","), "per month, and half of them are in households that cost less than that. We can say with 95% confidence that the true mean cost of housing per month for the population of MA residents is between $", prettyNum(summary_stats_contvar[3,3], digits = 3, big.mark = ","), "and $", prettyNum(summary_stats_contvar[3,4], digits = 3, big.mark = ","), ". The distribution appears to be skewed slightly right. Of the three continuous variables in this dataset, this one is the closests to having a normal distribution. However, this dataset only includes residents who pay more than $0 in monthly housing costs.")

ggplot(person_data,
       aes(x = monthly_housing_total)) +
  geom_histogram() +
  scale_x_continuous(name = "Household Income",
                     breaks = seq(0,8000,by = 1000),
                     labels = c("$0","$1,000","$2,000","$3,000","$4,000","$5,000","$6,000","$7,000","$8,000")) +
  scale_y_continuous(name = "Number of MA Residents in Sample") +
  theme_classic() +
  annotate("text", x = 3500, y = 6000, size = 4,
           label = paste("Population mean (95% confidence): $",
                         prettyNum(summary_stats_contvar[3,3], digits = 3, big.mark = ","),
                         "to $",
                         prettyNum(summary_stats_contvar[3,4], digits = 3, big.mark = ","),
                         "\nSample mean: $",
                         prettyNum(summary_stats_contvar[3,1], digits = 3, big.mark = ","),
                         "\nSample median: $",
                         prettyNum(median(person_data$monthly_housing_total), digits = 3, big.mark = ","),
                         "\nSample standard deviation: $",
                         prettyNum(summary_stats_contvar[3,2], digits = 3, big.mark = ","),
                         "\nSample interquartile range: $",
                         prettyNum(quantile(person_data$monthly_housing_total)["25%"], digits = 4, big.mark = ","),
                         "to $",
                         prettyNum(quantile(person_data$monthly_housing_total)["75%"], digits = 4, big.mark = ",")),
           hjust = 0, vjust = 1)

```

# Categorical Variables

## Commute Mode of Transportation
```{r categorical}
attach(person_data)
transpo <- unique(transpo_mode)
transpo

car_truck_van <- t.test(transpo_mode == transpo[1])
subway <- t.test(transpo_mode == transpo[2])
walk <- t.test(transpo_mode == transpo[3])
railroad <- t.test(transpo_mode == transpo[4])
bus <- t.test(transpo_mode == transpo[5])
streetcar <- t.test(transpo_mode == transpo[6])
bicycle <- t.test(transpo_mode == transpo[7])
other <- t.test(transpo_mode == transpo[8])
taxi <- t.test(transpo_mode == transpo[9])
ferry <- t.test(transpo_mode == transpo[10])
motorcycle <- t.test(transpo_mode == transpo[11])

shares_transpo <- tibble(transpo = c("Car, Truck, or Van",
                             "Subway or elevated train",
                             "Walking",
                             "Railroad",
                             "Bus",
                             "Streetcar or trolley",
                             "Bicycle",
                             "Other mode",
                             "Taxi",
                             "Ferryboat",
                             "Motorcycle"),
                 `Share` = c(car_truck_van$estimate,
                             subway$estimate,
                             walk$estimate,
                             railroad$estimate,
                             bus$estimate,
                             streetcar$estimate,
                             bicycle$estimate,
                             other$estimate,
                             taxi$estimate,
                             ferry$estimate,
                             motorcycle$estimate),
                 Low = c(car_truck_van$conf.int[1],
                             subway$conf.int[1],
                             walk$conf.int[1],
                             railroad$conf.int[1],
                             bus$conf.int[1],
                             streetcar$conf.int[1],
                             bicycle$conf.int[1],
                             other$conf.int[1],
                             taxi$conf.int[1],
                             ferry$conf.int[1],
                             motorcycle$conf.int[1]),
                 High = c(car_truck_van$conf.int[2],
                             subway$conf.int[2],
                             walk$conf.int[2],
                             railroad$conf.int[2],
                             bus$conf.int[2],
                             streetcar$conf.int[2],
                             bicycle$conf.int[2],
                             other$conf.int[2],
                             taxi$conf.int[2],
                             ferry$conf.int[2],
                             motorcycle$conf.int[2]))

paste("Of the 11 various modes of transport that MA residents use for their commute, the one with the highest percentage of MA residents in our sample is Car, Truck, or Van, which about",
      prettyNum(shares_transpo[1,2]*100, digits = 2),
      "percent of the sample population uses. We can say with 95% confidence that the true percent of MA residents who use a car, truck, or van for their commute is between",
      prettyNum(shares_transpo[1,3]*100, digits = 3),
      "and",
      prettyNum(shares_transpo[1,4]*100, digits = 3),
      "percent.")

knitr::kable(shares_transpo, caption = "Proportions and 95-percent confidence intervals of MA residents' commute tranportation mode")

```

## Highest Level of Education

```{r education level attainment}
education<- unique(highest_education)
education

master<- t.test(highest_education == education[1])
associate<- t.test(highest_education == education[2])
reg_hs<- t.test(highest_education == education[3])
college_deg<- t.test(highest_education == education[4])
college_1yrnodeg<- t.test(highest_education == education[5])
grade11<- t.test(highest_education == education[6])
ged<- t.test(highest_education == education[7])
college_less1yr<- t.test(highest_education == education[8])
prof_deg<- t.test(highest_education == education[9])
none<- t.test(highest_education == education[10])
grade10<- t.test(highest_education == education[11])
doctorate<- t.test(highest_education == education[12])
grade7<- t.test(highest_education == education[13])
grade12_nodip<- t.test(highest_education == education[14])
grade9<- t.test(highest_education == education[15])
grade8<- t.test(highest_education ==  education[16])
grade6<- t.test(highest_education == education[17])
grade3<- t.test(highest_education == education[18])
grade4<- t.test(highest_education == education[19])
grade5<- t.test(highest_education == education[20])
grade2<- t.test(highest_education == education[21])
grade1<- t.test(highest_education == education[22])
kindergarten<- t.test(highest_education == education[23])
preschool<- t.test(highest_education == education[24])

shares_education <- tibble(education = c("Master's degree",
                                         "Associate's degree",
                                         "Regular high school diploma",
                                         "Bachelor's degree",
                                         "Some years of college credit, no degree",
                                         "Grade 11",
                                         "GED or alternative credential",
                                         "Some college, but less than 1 year",
                                         "Professional degree beyond a bachelor's degree",
                                         "No schooling completed",
                                         "Grade 10",
                                         "Doctorate degree",
                                         "Grade 7",
                                         "12th grade-no diploma",
                                         "Grade 9",
                                         "Grade 8",
                                         "Grade 6",
                                         "Grade 3",
                                         "Grade 4",
                                         "Grade 5",
                                         "Grade 2",
                                         "Grade 1",
                                         "Kindergarten",
                                         "Nursery school, preschool"),
                           `Share` = c(master$estimate,
                                       associate$estimate,
                                       reg_hs$estimate,
                                       college_deg$estimate,
                                       college_1yrnodeg$estimate,
                                       grade11$estimate,
                                       ged$estimate,
                                       college_less1yr$estimate,
                                       prof_deg$estimate,
                                       none$estimate,
                                       grade10$estimate,
                                       doctorate$estimate,
                                       grade7$estimate, 
                                       grade12_nodip$estimate,
                                       grade9$estimate,
                                       grade8$estimate,
                                       grade6$estimate,
                                       grade3$estimate,
                                       grade4$estimate,
                                       grade5$estimate,
                                       grade2$estimate,
                                       grade1$estimate,
                                       kindergarten$estimate,
                                       preschool$estimate),
                           Low = c(master$conf.int[1],
                                       associate$conf.int[1],
                                       reg_hs$conf.int[1],
                                       college_deg$conf.int[1],
                                       college_1yrnodeg$conf.int[1],
                                       grade11$conf.int[1],
                                       ged$conf.int[1],
                                       college_less1yr$conf.int[1],
                                       prof_deg$conf.int[1],
                                       none$conf.int[1],
                                       grade10$conf.int[1],
                                       doctorate$conf.int[1],
                                       grade7$conf.int[1], 
                                       grade12_nodip$conf.int[1],
                                       grade9$conf.int[1],
                                       grade8$conf.int[1],
                                       grade6$conf.int[1],
                                       grade3$conf.int[1],
                                       grade4$conf.int[1],
                                       grade5$conf.int[1],
                                       grade2$conf.int[1],
                                       grade1$conf.int[1],
                                       kindergarten$conf.int[1],
                                       preschool$conf.int[1]),
                           High = c(master$conf.int[2],
                                       associate$conf.int[2],
                                       reg_hs$conf.int[2],
                                       college_deg$conf.int[2],
                                       college_1yrnodeg$conf.int[2],
                                       grade11$conf.int[2],
                                       ged$conf.int[2],
                                       college_less1yr$conf.int[2],
                                       prof_deg$conf.int[2],
                                       none$conf.int[2],
                                       grade10$conf.int[2],
                                       doctorate$conf.int[2],
                                       grade7$conf.int[2], 
                                       grade12_nodip$conf.int[2],
                                       grade9$conf.int[2],
                                       grade8$conf.int[2],
                                       grade6$conf.int[2],
                                       grade3$conf.int[2],
                                       grade4$conf.int[2],
                                       grade5$conf.int[2],
                                       grade2$conf.int[2],
                                       grade1$conf.int[2],
                                       kindergarten$conf.int[2],
                                       preschool$conf.int[2]))
paste("Of the 24 various levels of education, the one with the highest percentage of MA residents in our sample is Bachelor's Degree, which about",
      prettyNum(shares_education[4,2]*100, digits = 2),
      "percent of the sample population holds. We can say with 95% confidence that the true percent of MA residents who hold a Bachelor's Degree as their highest level of education is between",
      prettyNum(shares_education[4,3]*100, digits = 3),
      "and",
      prettyNum(shares_education[4,4]*100, digits = 3),
      "percent.")

knitr::kable(shares_education, caption = "Proportions and 95-percent confidence intervals of MA residents' level of education")

```




# Visualize Categorical Variables

## Commute Mode of Transportation

```{r visualize categorical variables - transportation}
ggplot(shares_transpo,
       aes(x = transpo, y = Share, ymin = Low, ymax = High)) +
  geom_bar(stat = "identity", color = "purple") +
  geom_errorbar(width = 0.5) +
  theme_light() +
  scale_x_discrete(name = "Commute Mode of Transportation") +
  scale_y_continuous(name = "Percent of Population", labels = c("0%", "20%", "40%", "60%", "80%")) +
    theme_classic()+
  theme(axis.text.x = element_text(angle = -45, hjust = 0)) 

```

## Highest Level of Education

```{r visualize categorical variables - education}
ggplot(shares_education,
       aes(x = education, y = Share, ymin = Low, ymax = High)) +
  geom_bar(stat = "identity", color = "red") +
  geom_errorbar(width = 0.5) +
  theme_light() +
  scale_x_discrete(name = "Highest Level of Education") +
  scale_y_continuous(name = "Percent of Population", labels = c("0%", "10%", "20%", "30%")) +
    theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8))
```
