---
title: "Assignment5"
author: "Megan Willis-Jackson"
date: "10/8/2020"
output: 
  html_document:
    toc: yes
    toc_float: yes
    cerulean: yes
    code_folding: hide
---

# Load Libraries

```{r regression, message=F}
library(tidyverse)
library(jtools)
library(interactions)
library(knitr)
library(ggthemes)

```

# Clean Data

```{r clean data, message=F}
people<- read.csv("people.csv")
people<- people[,2:7]

education<- unique(people$highest_education)

people_mutated<- people %>%
  mutate(education_binary = case_when(
    highest_education == "Master's degree" ~ "Post HS",
    highest_education == "Associate's degree" ~ "Post HS",
    highest_education == "Regular high school deploma" ~ "HS/equivalent or less",
    highest_education == "Bachelor's degree" ~ "Post HS",
    highest_education == "1 or more years of college credit, no degree" ~ "Post HS",
    highest_education == "Grade 11" ~ "HS/equivalent or less",
    highest_education == "GED or alternative credential" ~ "HS/equivalent or less",
    highest_education == "Some college, but less than 1 year" ~ "HS/equivalent or less",
    highest_education == "Professional degree beyond a bachelor's degree" ~ "Post HS",
    highest_education == "No schooling completed" ~ "HS/equivalent or less",
    highest_education == "Grade 10" ~ "HS/equivalent or less",
    highest_education == "Doctorate degree" ~ "Post HS",
    highest_education == "Grade 7" ~ "HS/equivalent or less",
    highest_education == "12th grade - no diploma" ~ "HS/equivalent or less",
    highest_education == "Grade 9" ~ "HS/equivalent or less",
    highest_education == "Grade 8" ~ "HS/equivalent or less",
    highest_education == "Grade 6" ~ "HS/equivalent or less",
    highest_education == "Grade 3" ~ "HS/equivalent or less",
    highest_education == "Grade 4" ~ "HS/equivalent or less",
    highest_education == "Grade 5" ~ "HS/equivalent or less",
    highest_education == "Grade 2" ~ "HS/equivalent or less",
    highest_education == "Grade 1" ~ "HS/equivalent or less",
    highest_education == "Kindergarten" ~ "HS/equivalent or less",
    highest_education == "Nursery school, preschool" ~ "HS/equivalent or less",
    highest_education == "Regular high school diploma" ~ "HS/equivalent or less"
  ))

people_mutated$transpo_mode<- str_replace_all(people_mutated$transpo_mode, "Car, truck, or van", "1Car, truck, or van")

```

# Run Regression for Each Model

## Model 1

To start off, I will note that for Assignment 4, I had designated my dependent variable as the amount of time it takes a MA resident to commute to work. I had an r-squared value of ~0.12, so my variables did not predict the variance in travel time very well. As I thought more about the variables I collected, I realized that in fact it may make more sense to have housing costs as the dependent variable. Housing costs are often correlated with location from wherever the concentration of jobs may be (i.e., lower travel time). Oftentimes people may even choose where to live based on how it will affect their commute length. Therefore, I ran with housing costs as my dependent variable, and compare all new models to the model 1 below.

Below I run the regression to determine how one continuous variable, household income, is affected by two categorical variables, mode of transportation and whether the individual has an education higher than a high school degree or not, and two continuous variables, time spent traveling to work and monthly housing cost. This first model has an R-squared value of 0.249, meaning my assortment of variables predict just under 25% of the variances in monthly housing costs.

```{r run the regression, message=F}
options(scipen = 999)
model1 <- lm(monthly_housing_total ~ transpo_mode + education_binary + household_income + travel_time, 
            data = people_mutated)

summary(model1)
```

## Model 2

In the model below, I try log-transforming the household income variable. I think it would make sense to do this because as one's income increases, each additional dollar has less of an impact on their overall quality of life. Therefore, log-transforming the variable would indicate that each unit increase in income means a doubling of income, which likely leads to a substantial difference in quality of life for a much broader range of incomes (e.g., doubling one's income from $20k to $40k is a very big difference, as is (I would guess) doubling one's income from $100k to $200k). 

Ultimately, however, this model decreases the R-squared value from model 1, meaning the independent variables explain less of the variation in monthly housing costs for MA residents.

```{r model 2, message=F}

model2 <- lm(monthly_housing_total ~ transpo_mode + education_binary + log(household_income) + travel_time, 
            data = people_mutated)

summary(model2)

```

## Model 3

For model3, I have sorted the modes of transportation into four categories as opposed to the 11 that MA residents used. This yields an R-squared value of 0.248, which still isn't quite as high as model1 with no transformations. It does, however, make the results a lot easier to quickly interpret. We find that people who walk or bike to work on average pay about $280 more in monthly housing costs than people who drive to work, and people who take public transit pay about $210 more per month, all statistically significant at the 95% confidence level. 

```{r model 3, message=F}
people_mutated <- people_mutated %>%
  mutate(transpo_categories = case_when(
    transpo_mode == "1Car, truck, or van" ~ "1drive",
    transpo_mode == "Subway or elevated" ~ "public transit",
    transpo_mode == "Walked" ~ "walk/bike",
    transpo_mode == "Railroad" ~ "public transit",
    transpo_mode == "Bus or trolley bus" ~ "public transit",
    transpo_mode == "Streetcar or trolley car (carro publico in Puerto Rico)" ~ "public transit",
    transpo_mode == "Bicycle" ~ "walk/bike",
    transpo_mode == "Other method" ~ "other",
    transpo_mode == "Taxicab" ~ "1drive",
    transpo_mode == "Ferryboat" ~ "public transit",
    transpo_mode == "Motorcycle" ~ "1drive"))

model3 <- lm(monthly_housing_total ~ transpo_categories + education_binary + household_income + travel_time, 
            data = people_mutated)

summary(model3)


```

## Model 4

I would think that there is an interaction between people's modes of transportation and the speed with which they get to work; I will therefore next try test an interaction between the mode of transportation and travel time.

To me, this interaction is really quite interesting. While the regression results of the transportation mode variable without the interaction indicate at the 95% confidence level that people using each of the modes of transportation (walk/bike, public transit, and other) pay a couple of hundred dollars more in housing costs per month than a person who drives (all else being equal), as travel time increases, the average person pays more if they drive a car whereas their monthly housing costs decrease if they use any of the other mode categories.

This model also has an R-squared value of 0.249, almost equal to model1 in that they both explain almost 25% of the variances in monthly housing costs for MA residents. However, as this model provides additional useful information about the relationship between housing costs and the other variables, I will select this model.

```{r model 4, message=F}

model4 <- lm(monthly_housing_total ~ transpo_categories + education_binary + household_income + travel_time + transpo_categories:travel_time, 
            data = people_mutated)

summary(model4)

interact_plot(model4, 
              pred = travel_time, 
              modx = transpo_categories, 
              interval = T, 
              modx.labels = c("Drive", "Other mode", "Public Transit", "Walk or Bike"),
              legend.main = "Mode of Transportation", colors = "CUD") +
  scale_x_continuous(name = "Travel Time to Work (minutes)",
                     breaks = seq(0, 150, by = 30)) +
  scale_y_continuous(name = "Monthly Housing Costs ($)") +
  theme()

```

# Models Side-by-Side

The chart below makes it quite clear which of the models predict the dependent variable with the most accuracy. Three of the models are very similar (1, 3, and 4), while model 2 predicts almost two percent less of the variance in housing costs in our dataset.

```{r models side-by-side, message=F}
ModelFit <- tibble(model = c(1, 2, 3, 4),
                   R_square = c(summary(model1)$adj.r.squared,
                                summary(model2)$adj.r.squared,
                                summary(model3)$adj.r.squared,
                                summary(model4)$adj.r.squared))

ggplot(ModelFit, aes(x = model, y = R_square)) +
  geom_line() +
  scale_x_continuous(name = "",
                   breaks = breaks <- seq(1, 4, by = 1),
                   labels = paste("Model", breaks)) +
  scale_y_continuous(name = "Adjusted R-squared value\n") +
  theme_economist()



```