---
title: "Assignment 1"
author: "Megan Willis-Jackson"
date: "9/4/2020"
output: html_document
---


#Access Census Data
```{r load libraries}
library(tidycensus)
library(tidyverse)
```

##Finding Variables
###Example 1: Individual
```{r}
person_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "person", year == 2018, survey == "acs1")
```
###Example 2: Household
```{r}
hh_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "housing", year == 2018, survey == "acs1")
```
###Example 3: Area
```{r}
area_vars_2018 <- load_variables(2018,"acs1")
```
###Example 4: Area, 2010 census
```{r}
area_vars_2010 <- load_variables(2010,"sf1")
```
##Explore Variables
```{r}
census_variables_2018 <- unique(area_vars_2018$concept)
view(census_variables_2018)
```
#Selecting Variables
1. Means of Transportation to Work: Categorical. Code: JWTR
2. Travel time to work: Continuous. Code: JWMNP
3. Household income: Continuous. Code: HINCP
4. Educational attainment: Categorical. Code: SCHL
5. Monthly rent: Continuous. Code: RNTP
6. Monthly first mortgage: Continuous. Code: MRGP
7. Monthly second/junior mortgage: Continuous. Code: SMP

##Compile Selected Variables into Dataset
```{r compile variables}
person_data <- get_pums(variables = c("JWTR", 
                                      "JWMNP", 
                                      "HINCP", 
                                      "SCHL", 
                                      "RNTP",
                                      "MRGP",
                                      "SMP"),
                        state = "MA", 
                        year = 2018, 
                        survey = "acs1",
                        recode = TRUE) %>%
  filter(JWMNP > 0) %>%
  select(JWTR_label, SCHL_label, JWMNP, HINCP, RNTP, MRGP, SMP)

```
```{r rename variables}
colnames(person_data)<- c("transpo_mode","highest_education","travel_time","household_income","monthly_rent","monthly_first_mortgage","monthly_second_mortgage")
```

```{r create monthly housing cost}
person_data$monthly_housing_total<- person_data$monthly_rent + person_data$monthly_first_mortgage + person_data$monthly_second_mortgage

person_data <- person_data[-c(5:7)]
```

#Save csv
```{r}
write.csv(person_data,"people.csv")
```







