---
title: "Assignment 1"
author: "Megan Willis-Jackson"
date: "9/5/2020"
output: 
  html_document: 
    toc: yes
    theme: cerulean
---
# Summary
The unit of analysis is at the individual person level, although some variables (household income, monthly rent/mortgage) are reported at the household level. The dataset includes all MA residents who have a commute to work longer than 0 minutes. The dataset includes the individuals' modes of transportation to work (categorical), commute time (continuous), highest level of education attained (categorical), household income (continuous), and monthly cost of housing (continuous). There are 33,441 total observations in this dataset. 

# Access Census Data
```{r load libraries}
library(tidycensus)
library(tidyverse)
```

## Finding Variables
### Example 1: Individual
```{r}
person_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "person", year == 2018, survey == "acs1")
```
### Example 2: Household
```{r}
hh_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "housing", year == 2018, survey == "acs1")
```
### Example 3: Area
```{r}
area_vars_2018 <- load_variables(2018,"acs1")
```
### Example 4: Area, 2010 census
```{r}
area_vars_2010 <- load_variables(2010,"sf1")
```
## Explore Variables
```{r}
census_variables_2018 <- unique(area_vars_2018$concept)
view(census_variables_2018)
```
# Selecting Variables
1. Means of Transportation to Work: Categorical. Code: JWTR
2. Travel time to work: Continuous. Code: JWMNP
3. Household income: Continuous. Code: HINCP
4. Educational attainment: Categorical. Code: SCHL
5. Monthly rent: Continuous. Code: RNTP
6. Monthly first mortgage: Continuous. Code: MRGP
7. Monthly second/junior mortgage: Continuous. Code: SMP

## Compile Selected Variables into Dataset
```{r compile variables}
person_data <- get_pums(variables = c("JWTR", 
                                      "JWMNP", 
                                      "HINCP", 
                                      "SCHL", 
                                      "RNTP",
                                      "MRGP",
                                      "SMP"),
                        state = "MA", 
                        year = 2018, 
                        survey = "acs1",
                        recode = TRUE) %>%
  filter(JWMNP > 0) %>%
  select(JWTR_label, SCHL_label, JWMNP, HINCP, RNTP, MRGP, SMP)

```
```{r rename variables}
colnames(person_data)<- c("transpo_mode","highest_education","travel_time","household_income","monthly_rent","monthly_first_mortgage","monthly_second_mortgage")
```

```{r create monthly housing cost}
person_data$monthly_housing_total<- person_data$monthly_rent + person_data$monthly_first_mortgage + person_data$monthly_second_mortgage

person_data <- person_data[-c(5:7)]
```

# Save csv
```{r save csv}
write.csv(person_data,"people.csv")
```

# Print example rows of dataset
```{r print rows}
print(person_data[700:709,1:5])
```





